---
title: "P8105 Homework 1 Submission"
author: "Rebecca Shyu"
date: 2019-09-12
output: github_document
---

[Homework Assignment Details](https://p8105.com/homework_1.html)

Problem 0.1:

* Create a public GitHub repo + local R Project (p8105_hw1_rs4338)
* Create a single .Rmd file named p8105_hw1_rs4338.rmd that renders to github_document
* Submit a link to your repo via Courseworks: (https://github.com/rysgpd/p8105_hw1_rs4338)

```{r setup, include = FALSE}
library(tidyverse)
```

Problem 1:

* Load the Palmer Penguins dataset
* Describe the `penguins` dataset
  + Names/Variables: 
      - Species (Adelie, Chinstrap, Gentoo)
      - Island (Biscoe, Dream, Torgersen)
      - Bill Length (in mm)
      - Bill Depth (in mm)
      - Flipper Length (in mm)
      - Body Mass (in g)
      - Sex (Female, Male)
      - Year (2007, 2008, 2009) 
  + Size of the dataset: 344 rows, 8 columns/variables
  + Mean Flipper Length: 200.9152 mm


```{r PalmerPenguins_exploratory}

data("penguins", package = "palmerpenguins")

# code to get all column names
columns_names = colnames(penguins)

# code to find the notable values of categorial variables
species_types = unique(penguins$species)
island_types = unique(penguins$island)
sex_types = unique(penguins$sex)
years_included = unique(penguins$year)

# code to find the number of rows and columns
col_num = ncol(penguins)
row_num = nrow(penguins)

# code to find the mean flipper length
mean_flipper_length = mean(penguins$flipper_length_mm, na.rm = TRUE)


plot_df = tibble(
  x = rnorm(1000, sd = .5),
  y = 1 + 2 * x + rnorm(1000)
)
```

First we show a histogram of the `x` variable.

```{r x_hist}
ggplot(plot_df, aes(x = x)) + geom_histogram()
```

Next we show a scatterplot of `y` vs `x`. 

```{r yx_scatter}
ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```
